Lens Modeling in \sw

### 2013-11-17 text/tex/intro.tex
testing 2
Update intro.tex
spelling modifications

@@

How to find gravitational lenses? Huge amount of image data from surveys that needs to be processed.
Even more coming in the future with new surveys \needcite
Robotic procession has been suggested \needcite, and tested \needcite, but has failed so far to be convincing \needcite.
Another suggestion involves humans, volunteers \footnote{A volunteer is considered everybody that has no background in astro physics.}.
\sw uses this approach with great success so far.\needcite

Next step involves modeling. that needs advanced knolegde and takes a lot of time.
Too much time to be done by astronomers them selves as the results from new surveys and identifiers like \sw come in.
So there is a demand of a means to modell a great amount of identified lens data, that scales with increasing data amount.

The purpose of this study was to provide a means to model a large amount of gravitational lenses by showing that gravitational lens modelling can be learned / done by volunteers.
We suggest, that volunteers will be as successful as professionals with modelling if provided with an easy to use tool with visual feedback (What you see is what you get, WYSIWYG) and a minimal set of instructions.
Volunteers will then crowd work (using buzz word here ;) ) / work collaborative on modelling lenses from several sources / groups at a central place.
Since this is a iterative learning process, the more involved volunteers will quickly gain knowledge that can be passed down to new volunteers.
That creates a social structure that scales well with the number of volunteers, as other projects\needcite have already shown.
Finding people working as volunteers has been shown to be successful last but not least by \sw and the whole galaxy zoo project.
To test the peoples abilities, we investigated the performance of a first set of volunteers modelling a set of simulated lenses.
We tested the ability to correctly identify lensed images and reproduce similar mass maps of the lens.

>>>>

This is my new Text

@@

How to find gravitational lenses? Huge amount of image data from surveys that needs to be processed.
Even more coming in the future with new surveys \needcite
Robotic processing has been suggested \needcite, and tested \needcite, but has failed so far to be convincing \needcite.
Another suggestion involves humans, volunteers \footnote{A volunteer is considered everyone that has no background in astro physics.}.
\sw uses this approach with great success so far.\needcite

Next step involves modeling. that needs advanced knowlegde and takes a lot of time.
Too much time to be done by astronomers themselves as the results from new surveys and identifiers like \sw come in.
So there is a demand of a means to model a great number of identified lens data, that scales with increasing volume of data.

The purpose of this study was to provide a means to model a large number of gravitational lenses by showing that gravitational lens modeling can be learned / done by volunteers.
We suggest, that volunteers will be as successful as professionals with modelling if provided with an easy to use tool with visual feedback (What you see is what you get, WYSIWYG) and a minimal set of instructions.
Volunteers will then crowd work (using buzz word here ;) ) / work collaborative on modeling lenses from several sources / groups at a central place.
Since this is an iterative learning process, the more involved volunteers will quickly gain knowledge that can be passed down to new volunteers.
That creates a social structure that scales well with the number of volunteers, as other projects\needcite have already shown.
Finding people working as volunteers has been shown to be successful last but not least by \sw and the whole galaxy zoo project.
To test the people's abilities, we investigated the performance of a few volunteers modeling a set of simulated lenses.
We tested the ability to correctly identify lensed images and reproduce similar mass map of the lens.
